Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-06 ms.tex
Clarified description of redshift-space distortions

We model the velocities of satellite galaxies as a Gaussian whose 
first moment is the host halo velocity and whose second moment is the 
solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
\begin{equation}
\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
\end{equation}
where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
In this way, we model the influence of redshift-space distortions on our predicted 
two-point functions.

>>>>

We model the radial velocity distribution of satellite galaxies as a Gaussian with 
first moment equal to the host halo velocity and second moment equal to the 
solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
\begin{equation}
\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
\end{equation}
where $\tilde{r} = r/\rvir,$ $g(x) = \rm{ln}(1+x) - x / (1+x),$ and $V_{\rm vir}^{2} = G\mvir/\rvir.$ 
We assume that velocities are isotropic, setting peculiar velocities in the simulation $z$-dimension  
equal to random draws from the above distribution. We place mock galaxies 
into redshift-space by replacing each galaxy's $z$-coordinate with $z \rightarrow z + V_{\rm z}/H_0.$
